D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-01 ootavacuous.tex
Call out older single-variable perturbation citation
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Suppose that in some execution of the previous example,
both \co{y} and \co{z} are zero.
Then changes to either \co{y} or \co{z}
will not cause a change in the value stored to \co{x}.
In other words, in this execution there is no semantic dependency
from either \co{y} or \co{z} to \co{x}.
But there \emph{is} a semantic dependency from the \emph{pair}
\{\co{y},~\co{z}\} to \co{x},
because changes to both \co{y} and \co{z}
can cause the value stored in \co{x} to change.
This means that accurate definitions of sdep cannot always rely on
single-variable perturbations;
they must consider changes to multiple variables.
See Appendix~\ref{app:Non-Trivial Semantic Dependencies}
for examples and additional discussion.

>>>>

Suppose that in some execution of the previous example,
both \co{y} and \co{z} are zero.
Then changes to either \co{y} or \co{z}
will not cause a change in the value stored to \co{x}.
In other words, in this execution there is no semantic dependency
from either \co{y} or \co{z} to \co{x}.
But there \emph{is} a semantic dependency from the \emph{pair}
\{\co{y},~\co{z}\} to \co{x},
because changes to both \co{y} and \co{z}
can cause the value stored in \co{x} to change.
This means that, prior work~\cite{PaulEMcKenney2016OOTA}
notwithstanding, accurate definitions of sdep cannot always rely on
single-variable perturbations;
they must consider changes to multiple variables.
See Appendix~\ref{app:Non-Trivial Semantic Dependencies}
for examples and additional discussion.
